---
documentclass: jss
author:
  - name: Young Geun Kim
    orcid: 0000-0001-8651-1167
    affiliation: Sungkyunkwan University
    # use this syntax to add text on several lines
    address: |
      | Department of Statistics
      | Sungkyunkwan University
      | Seoul, 03063, Korea
    email: \email{dudrms33@g.skku.edu}
    url: https://ygeunkim.github.io
  - name: Changryong Baek
    # orcid: 0000-0000-0000-0000
    affiliation: Sungkyunkwan University
    address: |
      | Department of Statistics
      | Sungkyunkwan University
      | Seoul, 03063, Korea
    # address: >
    #   Department of Statistics
    #   Sungkyunkwan University
    #   Seoul, 03063, Korea
    # To add another line, use \AND at the end of the previous one as above
  # - name: Third Author
  #   orcid: 0000-0000-0000-0000
  #   address: |
  #     | Department of Statistics and Mathematics,
  #     | Faculty of Biosciences,
  #     | Universitat Autònoma de Barcelona
  #   affiliation: |
  #     | Universitat Autònoma 
  #     | de Barcelona
  #   # use a different affiliation in adress field (differently formated here)
  #   affiliation2: Universitat Autònoma de Barcelona
title:
  formatted: "Bayesian Modeling of Multivariate Time Series Using \\pkg{bvhar} Package in \\proglang{R}"
  # If you use tex in the formatted title, also supply version without
  plain:     "Bayesian Modeling of Multivariate Time Series Using bvhar Package in R"
  # For running headers, if needed
  short:     "\\pkg{bvhar}: Bayesian Modeling of Multivariate Time Series"
abstract: >
  The abstract of the article.
keywords:
  # at least one keyword must be supplied
  formatted: [vector autoregressive model, vector heterogeneous autoregressive model, bayesian vector heterogeneous autoregressive model, bayesian vector autoregressiv model, time series, forecast, "\\proglang{RcppEigen}", "\\proglang{R}"]
  plain:     [vector autoregressive model, vector heterogeneous autoregressive model, bayesian vector heterogeneous autoregressive model, bayesian vector autoregressiv model, time series, forecast, RcppEigen, R]
preamble: >
  \usepackage{amsmath}
  \usepackage{orcidlink,thumbpdf,lmodern}
  \newcommand{\calW}{{\mathcal W}}
  \newcommand{\bbA}{{\mathbb A}}
  \newcommand{\bbB}{{\mathbb B}}
  \newcommand{\bbW}{{\mathbb W}}
  \newcommand{\bbE}{{\mathbb E}}
  \newcommand{\bbZ}{{\mathbb Z}}
  \newcommand{\bbR}{{\mathbb R}}
  \newcommand{\bbN}{{\mathbb N}}
  \newcommand{\bbC}{{\mathbb C}}
  \newcommand{\bbL}{{\mathbb L}}
  \newcommand{\bbP}{{\mathbb P}}
  \newcommand{\bbQ}{{\mathbb Q}}
  \newcommand{\bbF}{{\mathbb F}}
  \newcommand{\bbX}{{\mathbb X}}
  \newcommand{\bfa}{{\mathbf a}}
  \newcommand{\bfb}{{\mathbf b}}
  \newcommand{\bfd}{{\mathbf d}}
  \newcommand{\bfT}{{\mathbf T}}
  \newcommand{\bfA}{{\mathbf A}}
  \newcommand{\bfB}{{\mathbf B}}
  \newcommand{\bfX}{{\mathbf X}}
  \newcommand{\bfU}{{\mathbf U}}
  \newcommand{\bfY}{{\mathbf Y}}
  \newcommand{\bfy}{{\mathbf y}}
  \newcommand{\bfx}{{\mathbf x}}
  \newcommand{\bfu}{{\mathbf u}}
  \newcommand{\bfV}{{\mathbf V}}
  \newcommand{\bfv}{{\mathbf v}}
  \newcommand{\bfW}{{\mathbf W}}
  \newcommand{\bfw}{{\mathbf w}}
  \newcommand{\bfZ}{{\mathbf Z}}
  \newcommand{\bfz}{{\mathbf z}}
  \newcommand{\bfR}{{\mathbf R}}
  \newcommand{\bfh}{{\mathbf h}}
  \newcommand{\bfr}{{\mathbf r}}
  \newcommand{\bfN}{{\mathbf N}}
  \newcommand{\bfC}{{\mathbf C}}
  \newcommand{\bfc}{{\mathbf c}}
  \newcommand{\bfp}{{\mathbf p}}
  \newcommand{\bfgamma}{{\boldsymbol \gamma}}
  \newcommand{\bfeps}{{\boldsymbol \epsilon}}
  \newcommand{\bfmu}{{\boldsymbol \mu}}
  \newcommand{\bbphi}{\mathbb \Phi}
  \newcommand{\autocov}[1]{\Gamma(#1)}
  \newcommand{\calA}{\mathcal{A}}
  \newcommand{\calM}{\mathcal{M}}
  \newcommand{\calH}{\mathcal{H}}
  \newcommand{\calK}{\mathcal{K}}
  \newcommand{\calP}{\mathcal{P}}
  \newcommand{\sfA}{\mathsf{A}}
  \newcommand{\sfB}{\mathsf{B}}
  \newcommand{\designvhar}{\mathbb{X}_1}
  \newcommand{\designvar}{\mathbb{X}_0}
  \newcommand{\response}{\mathbb{Y}_0}
  \newcommand{\error}{\mathbb{Z}_0}
  \newcommand{\designbvhar}{\mathbb{X}_\ast}
  \newcommand{\responsebvharS}{\mathbb{Y}_\ast}
  \newcommand{\responsebvharL}{\mathbb{Y}_{\#}}
  \newcommand{\designdummy}{\mathbb{X}_H}
  \newcommand{\responsedummy}{\mathbb{Y}_H}
  \newcommand{\designLdummy}{\mathbb{X}_L}
  \newcommand{\responseLdummy}{\mathbb{Y}_L}
  \newcommand{\errorbvharS}{\mathbb{Z}_\ast}
  \newcommand{\errorbvharL}{\mathbb{Z}_{\#}}
  \newcommand{\errordummy}{\mathbb{Z}_H}
  \newcommand{\errorLdummy}{\mathbb{Z}_L}
  \newcommand {\normal}{{\mathcal N}}
  \newcommand {\MN}{{\mathcal {MN}}}
  \newcommand {\IW}{{\mathcal {IW}}}
  \newcommand {\wishart}{{\mathcal {W}}}
  \newcommand {\IG}{{\mathcal {IG}}}
  \newcommand {\gamdistn}{{\mathcal {G}}}
  \newcommand {\ber}{{\mathcal {Ber}}}
  \newcommand {\cauchy}{{\mathcal {C}}}
  \newcommand{\bedistn}{\mathcal{Beta}}
  \newcommand{\scolon}{\mathpunct{;}}
  \newcommand{\defn}{\mathpunct{:=}}
  \newcommand{\distn}{\stackrel{\mathcal{D}}{=}}
  \newcommand{\zero}{\mathbf{0}}
  \newcommand{\one}{\mathbf{1}}
  \newcommand{\diag}{\mathrm{diag}}
  \newcommand{\cterm}{\text{if constant term exists}}
  \newcommand{\cnot}{\text{if constant term does not exist}}
  \newcommand{\iid}{\stackrel{\mathrm{iid}}{\sim}}
  \newcommand{\indep}{\stackrel{\mathrm{indep}}{\sim}}
  \newcommand{\priormean}{M_0}
  \newcommand{\priormnscale}{\Omega_0}
  \newcommand{\prioriwscale}{\Psi_0}
  \newcommand{\prioriwdf}{\nu_0}
  \newcommand{\marginaldistn}[1]{\left( #1 \right)}
  \newcommand{\condndistn}[2]{\left( #1 \mid #2 \right)}
  \newcommand{\marginaldensity}[1]{\left[ #1 \right]}
  \newcommand{\condndensity}[2]{\left[ #1 \mid #2 \right]}
  \newcommand{\tr}{\prime}
  \newcommand{\bbY}{{\mathbb Y}}
  \newcommand{\bfalpha}{{\boldsymbol \alpha}}
  \newcommand{\bfphi}{{\boldsymbol \phi}}
  \newcommand{\bfeta}{{\boldsymbol \eta}}
  \newcommand{\bfomega}{{\boldsymbol \omega}}
  \newcommand{\bfpsi}{{\boldsymbol \psi}}
  \newcommand{\bfrho}{{\boldsymbol \rho}}
bibliography: refs.bib
vignette: >
  %\VignetteIndexEntry{Bayesian Modeling for Multivariate Time Series Using bvhar in R (Kim & Baek)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output: rticles::jss_article
---

```{r, setup, include=FALSE}
# options(prompt = 'R> ', continue = '+ ')
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
```

```{r load-bvhar, echo=FALSE, message=FALSE}
library(bvhar)
```

# Introduction

<!-- This template demonstrates some of the basic LaTeX that you need to know to create a JSS article. -->

<!-- ## Code formatting -->

<!-- In general, don't use Markdown, but use the more precise LaTeX commands instead: -->

<!-- * \proglang{Java} -->

<!-- * \pkg{plyr} -->

<!-- One exception is inline code, which can be written inside a pair of backticks (i.e., using the Markdown syntax). -->

<!-- If you want to use LaTeX commands in headers, you need to provide a `short-title` attribute. You can also provide a custom identifier if necessary. See the header of Section \ref{r-code} for example. -->

<!-- # \proglang{R} code {#r-code short-title="R code"} -->

<!-- Can be inserted in regular R markdown blocks. -->

<!-- ```{r} -->

<!-- x <- 1:10 -->

<!-- x -->

<!-- ``` -->

<!-- ## Features specific to \pkg{rticles} {short-title="Features specific to rticles"} -->

<!-- * Adding short titles to section headers is a feature specific to \pkg{rticles} (implemented via a Pandoc Lua filter). This feature is currently not supported by Pandoc and we will update this template if [it is officially supported in the future](https://github.com/jgm/pandoc/issues/4409). -->

<!-- * Using the `\AND` syntax in the `author` field to add authors on a new line. This is a specific to the `rticles::jss_article` format. -->

In multivariate time series task, we want to forecast or structurally analyze. @banbura2010 had shown that BVAR models can improve forecasting as well as provide realistic structural analysis based on its shrinkage structure.

# Econometric framework {#sec:econ}

\pkg{bvhar} deals with various types of models, including vector autoregressive (VAR) models and vector heterogeneous autoregressive (VHAR) models; both frequentist and Bayesian approaches. In this section, we specify these models and introduce prior distributions used in Bayesian modeling.

## Vector autoregressive and heterogeneous autoregressive models {#sec:vhar short-title="VHAR"}

We are interested in modeling the $k$-dimensional daily time series $\{ \bfY_t = (Y_{1t}, Y_{2t}, \ldots, Y_{kt})^\tr \colon i = 1, 2, \ldots, T \}$. VAR model of lag $p$ (VAR($p$)) is one of the most popular model. We formulate the model as follows.

\begin{equation}
  \bfY_t = \bfc + A_1 \bfY_{t - 1} + \cdots + A_p \bfY_{t - p} + \bfeps_t
  \label{eq:vareq}
\end{equation}

where $\bfeps_t$ is innovation vector series following multivariate normal distribution of mean zero.


\begin{equation}
  \bfY_t = \bfc + \Phi^{(d)} \bfY_{t - 1} + \Phi^{(w)} \bfY_{t - 1}^{(w)} + \Phi^{(m)} \bfY_{t - 1}^{(m)} + \bfeps_t
  \label{eq:vhareq}
\end{equation}


## Minnesota priors {#sec:minnesota short-title="minn"}

## Stochastic volatility models {#sec:sv short-title="sv"}

## Continuous shrinkage priors {#sec:shrinkage short-title="shrinkage"}

# The \pkg{bvhar} package {#sec:bvharpkg short-title="package"}

